%% ================================================================================
%% This LaTeX file was created by AbiWord.                                         
%% AbiWord is a free, Open Source word processor.                                  
%% More information about AbiWord is available at http://www.abisource.com/        
%% ================================================================================

\documentclass[a4paper,portrait,12pt]{article}
\usepackage[latin1]{inputenc}
\usepackage{calc}
\usepackage{setspace}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[normalem]{ulem}
%% Please revise the following command, if your babel
%% package does not support zh-CN
\usepackage[zh]{babel}
\usepackage{color}
\usepackage{hyperref}
 
\begin{document}


\begin{flushleft}
MAT8010 Homework \#3
\end{flushleft}


\begin{flushleft}
Due Date: April 3, 2018
\end{flushleft}


\begin{flushleft}
1. (3 points) Find a closed form expression for each of the following generating functions:
\end{flushleft}


\begin{flushleft}
(a)
\end{flushleft}





\begin{flushleft}
P$\infty$
\end{flushleft}





\begin{flushleft}
+ 2)2 xn ,
\end{flushleft}





\begin{flushleft}
(b)
\end{flushleft}





\begin{flushleft}
P$\infty$
\end{flushleft}





\begin{flushleft}
+ 2)2 xn! ,
\end{flushleft}





\begin{flushleft}
(c)
\end{flushleft}





\begin{flushleft}
P$\infty$
\end{flushleft}





\begin{flushleft}
n=0 (n
\end{flushleft}


\begin{flushleft}
n=0 (n
\end{flushleft}





2


\begin{flushleft}
n=0 (n + 2)
\end{flushleft}





\begin{flushleft}
n
\end{flushleft}





? ?


\begin{flushleft}
2n
\end{flushleft}


\begin{flushleft}
n
\end{flushleft}





\begin{flushleft}
xn .
\end{flushleft}





\begin{flushleft}
2. (2 points) Problem 14K, page 149 (Van Lint/Wilson).
\end{flushleft}


\begin{flushleft}
3. (2 points) Let n be a positive integer, q a prime power, and let f2 (n, q)=the number
\end{flushleft}


\begin{flushleft}
of co-prime pairs of monic polynomials of degree n over GF(q). Find a simple formula for
\end{flushleft}


\begin{flushleft}
f2 (n, q).
\end{flushleft}


\begin{flushleft}
4. (3 points) An L-tile is a 2 × 2 square with the upper right 1 × 1 square removed;
\end{flushleft}


\begin{flushleft}
no rotations are allowed. Let an be the number of tilings of a 4 × n rectangle using tiles
\end{flushleft}


\begin{flushleft}
that are either 1 × 1 squares or L-tiles. Find a closed form for the generating function
\end{flushleft}


\begin{flushleft}
1 + a1 x + a2 x2 + a3 x3 + · · · (i.e., write the generating function as a rational function).
\end{flushleft}


\begin{flushleft}
5. For positive integers m and n, let f (m, n) denote the number of n-tuples (x1 , x2 , . . . , xn )
\end{flushleft}


\begin{flushleft}
of integers such that
\end{flushleft}


\begin{flushleft}
|x1 | + |x2 | + · · · + |xn | $\leq$ m.
\end{flushleft}


\begin{flushleft}
(a). (2 points) Find a recurrence formula for f (m, n).
\end{flushleft}


\begin{flushleft}
(b). (1 point) Use the recurrence formula to prove that f (m, n) = f (n, m).
\end{flushleft}


\begin{flushleft}
(c). (1 point) Do part (b) by using the generating function method.
\end{flushleft}


\begin{flushleft}
(d). (2 points) Find a closed formula for
\end{flushleft}





\begin{flushleft}
P
\end{flushleft}





\begin{flushleft}
n$\geq$0
\end{flushleft}





1





\begin{flushleft}
f (n, n)xn .
\end{flushleft}





\newpage



\end{document}
